On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-14 MS.tex
fix fig labl and map some editing on ms

We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth  rate (Table \ref{tab:trade-offs}) . We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers. Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters). While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e. title, keywords, and abstracts, \citealt{Beckmann:2012hn}). This limitation does not apply to Google Scholar, where all text that is electronically available on the internet is indexed.

@@

Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate. On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).  On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approximately 18900 papers. We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''. All searches were conducted between March and December 2014.

@@

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications (coloured lines), compared to standardised thresholds used in the analysis (black lines). Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. The solid vertical lines indicate the thresholds used to classify plants in one of three stages. Studies mark with a ``*'' were those where stage was changed, compared to the original publication. Studies marked with ``+'' are those where plants came from different growth form.}
% TODO: Anais -- what does different growth form mean?
\label{fig:fig2}
\end{figure}

@@

\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}

>>>>

We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth rate (Table \ref{tab:trade-offs}). We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers. Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters). While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e. title, keywords, and abstracts, \citealt{Beckmann:2012hn}). This limitation does not apply to Google Scholar.

@@

Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate. On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approximately 18900 papers. We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''. All searches were conducted between March and December 2014.

@@

% TO DO : maybe explain in one sentence that mixing RGR and AGR is not a heresy here because we are not expecting different pattern with RGR vs AGR except for seedmass in seedling

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications (coloured lines), compared to standardised thresholds used in the analysis (black lines). Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. The solid vertical lines indicate the thresholds used to classify plants in one of three stages. Studies mark with a ``*'' were those where stage was changed or assigned, compared to the original publication. }
\label{fig:fig2}
\end{figure}

@@

\clearpage
\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}
